---
title: 'Statistical Inference Course Project (Part 1)'
author: "Tong Tat"
date: "December 22, 2017"
output:
  pdf_document: default
  html_document:
    highlight: tango
    keep_md: yes
    theme: yeti
---

**Rpub Link:** [Click Here](http://rpubs.com/chuatt/343747)

# Part 1
## 1.1. Overview

This is a document for Coursera Statistical Inference Course Final Project. This project will investigate the exponential distribution in R and compare it with the Central Limit Theorem. Given that lambda = 0.2 for all of the simulations. Part 1 of the project will investigate the distribution of averages of 40 exponentials over a thousand simulations.


## 1.2. Simulations

```{r, warning=FALSE, echo=TRUE, cache=FALSE, message=FALSE}
# Using pre-defined parameters
lambda <- 0.2
n <- 40
sims <- 1:1000
set.seed(123)

# Check for missing dependencies and load necessary R packages
if(!require(ggplot2)){install.packages('ggplot2')}; library(ggplot2)

# Simulate the population
population <- data.frame(x=sapply(sims, function(x) {mean(rexp(n, lambda))}))

# Plot the histogram
hist.pop <- ggplot(population, aes(x=x)) + 
  geom_histogram(aes(y=..count.., fill=..count..)) +
  labs(title="Histogram for Averages of 40 Exponentials over 1000 Simulations", y="Frequency", x="Mean")
hist.pop
```


## 1.3. Sample Mean versus Theoretical Mean

As we can see below, both sample mean and theoretical mean are very close. 
```{r, warning=FALSE, echo=TRUE, cache=FALSE, message=FALSE}
# Tabulating the Sample Mean & Theoretical Mean
sample.mean <- mean(population$x)
theoretical.mean <- 1/lambda
cbind(sample.mean, theoretical.mean)

# Checking 95% confidence interval for Sample Mean
t.test(population$x)[4]

```


At 95% confidence interval, the sampled mean is between `r t.test(population$x)$conf.int[1]` and `r t.test(population$x)$conf.int[2]`.


## 1.4. Sample Variance versus Theoretical Variance

As we can see below both Sample Variance and Theoretical Variance are very close.
```{r, warning=FALSE, echo=TRUE, cache=FALSE, message=FALSE}
sample.variance <- var(population$x)
theoretical.variance <- ((1/lambda)^2)/n
cbind(sample.variance, theoretical.variance)

```


## 1.5. Distribution

```{r, warning=FALSE, echo=TRUE, cache=FALSE, message=FALSE}
# Plotting Sample Mean & Varience vs Theoretical Mean & Varience
gg <- ggplot(population, aes(x=x)) +
  geom_histogram(aes(y=..density.., fill=..density..)) +
  labs(title="Histogram of Averages of 40 Exponentials over 1000 Simulations", y="Density", x="Mean") + 
  geom_density(colour="blue") +
  geom_vline(xintercept=sample.mean, colour="blue", linetype="dashed") +
  stat_function(fun=dnorm,args=list( mean=1/lambda, sd=sqrt(theoretical.variance)),color = "red") +
  geom_vline(xintercept=theoretical.mean, colour="red", linetype="dashed") 
gg

```


As we can see, the Sampled mean for 40 exponentials simulated 1000 times are very close to the Theoretical mean for a normal distribution.

Please note the assumptions is we are sampling without replacement and set.seed is at 123.



