---
title: 'Statistical Inference Course Project (Part 2)'
author: "Tong Tat"
date: "December 23, 2017"
output:
  html_document:
    highlight: tango
    keep_md: yes
    theme: yeti
  pdf_document: default
---

**Rpub Link:** [Click Here](http://rpubs.com/chuatt/344126)


# Part 2
For the second part of the project, we are going to analyze the ToothGrowth data in the R datasets package.


# 2.1. Loading Dataset
```{r, warning=FALSE, echo=TRUE, cache=FALSE, message=FALSE}
# Check for missing dependencies and load necessary R packages
if(!require(ggplot2)){install.packages('ggplot2')}; library(ggplot2)

# Load dataset
data("ToothGrowth")

# Quick explanation on ToothGrowth dataset
?ToothGrowth

# Check summary
summary(ToothGrowth)

# Display different summary
str(ToothGrowth)
```


# 2.2. Data Visualization

Now since "supp" is the Supplyment type (namely **VC** represents **Ascorbic Acid** and **OJ** represents **Orange Juice**), so it is easier to look at Tooth Length vs Dose breakdown by Supplyment type.

```{r, warning=FALSE, echo=TRUE, cache=FALSE, message=FALSE}
gg2 <- ggplot(ToothGrowth, aes(x=factor(dose), y=len, fill=factor(dose))) +
  geom_boxplot() + facet_grid(.~supp) +
  labs(title="Comparison of Different Supplyment Type for Different Vitamin Dose", y="Tooth Length", x="Dose (mg/day)") + scale_fill_discrete(name = "Dose") 
gg2
```


# 2.3. Calculating Confidence Interval
```{r, warning=FALSE, echo=TRUE, cache=FALSE, message=FALSE}
# Calculate Confidence Interval for Dose=0.5 mgrams/day.
dose.05 <- subset(ToothGrowth, dose==0.5)
test.05 <- t.test(len ~ supp, paired=F, var.equal=F, data=dose.05)


# Calculate Confidence Interval for Dose=0.5 mgrams/day.
dose.1 <- subset(ToothGrowth, dose==1)
test.1 <- t.test(len ~ supp, paired=F, var.equal=F, data=dose.1)


# Calculate Confidence Interval for Dose=0.5 mgrams/day.
dose.2 <- subset(ToothGrowth, dose==2)
test.2 <- t.test(len ~ supp, paired=F, var.equal=F, data=dose.2)


# Summarizing p-value and Confidence Interval in a table
table1 <- data.frame(
  "p.value"=c(test.05$p.value, test.1$p.value, test.2$p.value), 
  "Conf.Low"=c(test.05$conf.int[1], test.1$conf.int[1], test.2$conf.int[1]),
  "Conf.High"=c(test.05$conf.int[2], test.1$conf.int[2], test.2$conf.int[2]),
  row.names=c("Dose.05", "Dose.1", "Dose.2")
)
table1

```


# 2.4. Assumptions and Conclusion

For this ToothGrowth dataset, I assume the data is collected from random Guinea pigs given either Orange Juice or Asorbic Acid. Hence, when doing the t-test, we have to use paired=FALSE. I also assume the experiment is conducted on the same species of Guinea pigs, hence it is assumed to be no error term.

Based on the p-value, for Dose=0.05mg/day & 1mg/day, since the p-value is less than 5%, we reject the null hypothesis and conclude there is significant difference between Orange Juice and Ascorbic Acid at low dose (less than or equal 1mg/day). For Dose=2mg/day, since the p-value is greater than 5%, we failed to reject the null hypothesis and conclude there is no significant difference between Orange Juice and Ascorbic Acid at high dose (2mg/day).  
